---
title: "RLab1"
author: "Cedric Beaulac"
date: "April 23, 2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment=NA)
```

# Install R

## Clean way to work

- Set up a working directory

```{r include=TRUE}
setwd("C:/R/STA302")
```

- Make sure your data sets are in your working directory.

- You might want to have one directory per lab (project)

# Install package

## Google is your friend

- I will say this a lot.
- Let's try to see if a packaged contains our permutation rank test.

```{r include=TRUE}
#install.packages("exactRankTests")
library("exactRankTests")
x <- c(48,56,58)
y <- c(44,46,51)
```

---

## Help function

- Add ? after a function name to access help
- Google is your friend (again)

---

```{r include=TRUE}
perm.test(x,y)
```

---

## Help function

- Well that's not the 0.1 we expected!
- Use the help function again!

---

```{r include=TRUE}
perm.test(x,y,alternative='greater')
```

---

## Generating data set

- It is common in statistics and computer sciences to generate random data set to test our algorithms.
- It is easy to generate variable from multiple distribution in R.
- To generate a categorical variable use the \textit{sample} function.

---

```{r include=TRUE}
?sample
x1 = sample(seq(1:6),3,replace=TRUE)
x2 = sample(seq(1:6),3,replace=TRUE)
x1
x2
perm.test(x1,x2,alternative='greater')
```

## Generating data set

- The function \textif{rnorm} can be used for normal variable. 
- I invite you to google other populare distributions.

---

```{r include=TRUE}
#Write code down!
#Nothing was prepared in advance: THIS IS DANGEROUS!
#A prof taking risks!
```